---
title: "Network optimization Project"
author: "Afsar Ali"
output:
  prettydoc::html_pretty:
    theme: Cayman
    highlight: github
    toc: yes
    toc_depth: '4'
---

# Objective
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
# Course: BUAN 5260
# Title: Week 4-Network optimization
# Purpose: USE IFRC Information information to model scenarios 
#           and make Recommendation Plans
# Author: Afsar Ali

```

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
# Clear packages 
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(
  paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
  detach, character.only = TRUE, unload = TRUE)

# Clear all data in environment
rm(list=ls(all=TRUE))

# Load packages
library(igraph)
library(lpSolve)
library(lpSolveAPI)
library(tidyverse)
library(magrittr)
library(data.table)

set.seed(123)
```
#Loading and cleaning the data

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
#load Data 
ifrc <- read.csv("5260_S18_Aiding_Africa_Data.csv", skip = 1)
#Naming and Creating each table
req_trv <- ifrc[1:3,1:3]
mdata <- ifrc[,8:12]
req <- ifrc[1:9,14:15]
air_max <- ifrc[1:15,17:19]
truck_max <- ifrc[1:6,21:23]

#create nodes
req$Requirements <- req$Requirements *-1
req$City <- as.character(req$City)
nodes<- rbind('1' = c('New York, NY', '500000'), '2' = c('Jacksonville, FL', '500000'), req)
nodes$Requirements <- as.integer(nodes$Requirements)

# Join the tables and create edges

edges <- mdata %>%
  left_join(req_trv, by = c("Type.1" = "Type")) %>%
  mutate(Time = Distance / Speed) %>%
  mutate(Cost = Cost * 1000) %>%
  left_join(air_max, by = c("From" = "From.1", "To" = "To.1")) %>%
  left_join(truck_max, by = c("From" = "From.2", "To" = "To.2")) 
colnames(edges)[3] <- 'Type'

#create constraints
edges$Max.Airplanes <- edges$Max.Airplanes * edges$Capacity
edges$Max.Trucks <- edges$Max.Trucks * edges$Capacity
edges$Max.Airplanes[is.na(edges$Max.Airplanes)] <- 0
edges$Max.Trucks[is.na(edges$Max.Trucks)] <- 0
edges$Max <- edges$Max.Trucks + edges$Max.Airplanes
edges$Max[is.na(edges$Max)] <- 0

#Network ID
edges$ID <- paste(edges$From, edges$To, sep = ' > ')
```


#1 Netowrk Map
- Make sense all the Air Routes are the Fastest 
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
net <- graph_from_data_frame(d=edges, vertices=nodes, directed=T)

net$layout <- matrix(c(-800, -800,  
                       0,  0,  0, 0,  0, 0, 
                       800, 800, 800,
                       225, 125, 
                       300, 250, 200, 150, 100, 50, 
                       250, 175, 100), nc = 2)

#Set Weight for Edges
E(net)$weight = E(net)$Time
#Create a Unique col
edges$ID <- paste(edges$From, edges$To, sep = ' > ')
#Add route attribute
V(net)$route <- c("From","From","To","To","To","To","To","To","To","To","To")
V(net)$color <- c("gold","green")[1+(V(net)$route=="From")]
#look at the data
glimpse(edges)

# Get some colours in to visualise routes
E(net)$color[E(net)$Type == 'Truck'] <- 'saddlebrown'
E(net)$color[E(net)$Type == 'Airplane'] <- 'forestgreen'
E(net)$color[E(net)$Type == 'Ship'] <- 'royalblue'


#Plot Network Map
plot(net, edge.arrow.size=.3, edge.label = round(E(net)$Time, 2), 
     edge.width = 10*E(net)$Time/max(E(net)$Time),
     vertex.size=25)
```

#2 Netowrk Map with Fastest Route
-Bottlenecks are on Dakar, Senegal, Libreville, Garbon, Luanda, Angola
-Quickest route is 20.60 hours From New York to Ndjamena, Chad
+New York, NY     > Kosongo, D.R. Congo = 21.04             
+New York, NY     > Ndjamena, Chad      = 20.60         
+New York, NY     > Niamey, Niger       = 22.76
+Jacksonville, FL > Kosongo, D.R. Congo = 21.15             
+Jacksonville, FL > Ndjamena, Chad      = 20.71         
+Jacksonville, FL > Niamey, Niger       = 22.87 


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
#Create Table for shortest time
distMatrix <- shortest.paths(net, v=V(net), to=V(net))

as.data.frame(distMatrix)

all_shortest_paths(net, c("New York, NY", 'Jacksonville, FL'), 
                   c('Kosongo, D.R. Congo' ,"Ndjamena, Chad",
                     'Niamey, Niger'))$res[[1]]

# New York, NY  >  Khartoum, Sudan  >  Niamey, Niger  

distances(net, c("New York, NY", 'Jacksonville, FL'), 
                   c('Kosongo, D.R. Congo' ,"Ndjamena, Chad",
                     'Niamey, Niger'))

#                 Kosongo, D.R. Congo Ndjamena, Chad Niamey, Niger
#New York, NY                   21.04          20.60         22.76
#Jacksonville, FL               21.15          20.71         22.87

shortMatrix<- mst(net, weights = NULL)
shortMatrix
plot(shortMatrix, edge.arrow.size=.2, edge.label = round(E(net)$Time, 2))
```


#3 - 2nd Plan considering cost and constraints 


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
#Part 3 - Min Cost
# Set up model
min_cost <- make.lp(0, 30)
## Set objective fn 
obj_fn <- as.integer(as.vector(edges$Cost))
set.objfn(min_cost, obj_fn)
# Set up constraints
#Input
add.constraint(min_cost, c( 150, 240, 150, 150, 240, 240, 0  , 0  , 0  , 0  , 0   
                            , 0  , 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   , 0   , 0  , 0   , 0   , 0  , 0   , 0   ), "=", 500000)  #NY
add.constraint(min_cost, c( 0  , 0  , 0  , 0  , 0  , 0  , 150, 240, 150, 150, 240 
                            , 240, 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   , 0   , 0  , 0   , 0   , 0  , 0   , 0   ), "=", 500000)  #FL

#City Requirements 
add.constraint(min_cost, c(-150, 0  , 0  , 0  , 0  , 0  ,-150, 0  , 0  , 0  , 0   
                           , 0  , 150 , 0    , 0  , 0  , 0   , 0   , 150, 0   
                           , 0  , 0  , 0   , 0   , 150, 0   , 0   , 0  , 0   , 0   ), "=", -150000)  #Lusaka
add.constraint(min_cost, c( 0  ,-240, 0  , 0  ,  0  , 0  ,0   ,-240, 0  , 0  , 0  
                            , 0  , 0   , 0    , 0  , 0  , 0   , 0   , 0  ,17.7 
                            , 0  , 0  , 0   , 0   , 0  ,17.7 , 0   , 0  , 0   , 0   ), "=", -100000)  #Libreville
add.constraint(min_cost, c( 0  ,0   ,-150, 0  ,  0  , 0  ,0   ,0   ,-150, 0  , 0  
                            , 0  , 0   , 0    ,150 , 0  , 0   , 0   , 0  , 0   
                            ,150 , 0  , 0   , 0   , 0  , 0   , 150 , 0  , 0   , 0   ), "=", -120000)  #Nairobi
add.constraint(min_cost, c( 0  ,0   ,0   ,-150,  0  , 0  ,0   ,0   ,0   ,-150, 0  
                            , 0  , 0   , 0    , 0  ,150 , 0   , 0   , 0  , 0   
                            , 0  ,150 , 0   , 0   , 0  , 0   ,  0  , 150, 0   , 0   ), "=", -90000)   #Khartoum
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,-240 , 0  ,0   ,0   ,0   ,0   
                            ,-240, 0  , 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   
                            , 0  , 0  ,17.7 , 0   , 0  , 0   ,  0  , 0  ,17.7 , 0   ), "=", -130000)  #Luanda
add.constraint(min_cost, c( 0  ,0   ,0   ,0   , 0   ,-240,0   ,0   ,0   ,0   , 0  
                            ,-240, 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   ,17.7 , 0  , 0   ,  0  , 0  , 0   ,17.7 ), "=", -50000)   #Dakar
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,0    ,0   ,0   ,0   ,0   ,0   , 0  
                            ,0   ,-150 , 0    ,-150,-150, 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   , 0   , 0  , 0   ,  0  , 0  , 0   , 0   ), "=", -100000)  #Niamey Air routes only
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,0    ,0   ,0   ,0   ,0   ,0   , 0  
                            ,0   , 0   , 0    , 0  , 0  , 0   , 0   ,-150,-17.7,
                            -150,-150,-17.7,-17.7, 0  , 0   ,  0  , 0  , 0   , 0   ), "=", -180000)  #Kosongo
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,0    ,0   ,0   ,0   ,0   ,0   , 0  
                            ,0   , 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   
                            , 0  , 0  , 0   , 0   ,-150,-17.7,-150 ,-150,-17.7,-17.7), "=", -80000)  #Ndjamena

#additional constraint
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,0    ,0   ,0   ,0   ,0   ,0   , 0  
                            ,0   , 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   , 0   , 0  ,1 , 0   , 0  ,1 ,1), "<=", 840) #Ndjmamena Truck constraint
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,0    ,0   ,0   ,0   ,0   ,0   , 0  
                            ,0   , 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   , 0   ,1 , 0   , 0   , 0  , 0   , 0   ), "<=", (200)) #200 flights from tLusaka-Ndjmamena constrain
add.constraint(min_cost, c( 0  ,0   ,0   ,0   ,0    ,0   ,0   ,0   ,0   ,0   , 0  
                            ,0   , 0   , 0    , 0  , 0  , 0   , 0   , 0  , 0   , 0  
                            , 0  , 0   , 0   , 0  , 0   , 0   ,1 , 0   , 0   ), "<=", (200)) #200 flights from Khartoum-Ndjmamena constraint

#set names
dimnames(min_cost) <- list(c("New York", "Jacksonville","Lusaka", 
                             "Libreville", "Nairobi", "Khartoum", "Luanda", 
                             "Dakar", "Niamey", "Kosongo", "Ndjamena", 
                             "Ndjamena Truck Limit", "Lusaka->Ndjmamena limited Flights",
                             "Khartoum->Ndjmamena limited Flights"), as.vector(edges$ID) )

# Write to view the algebraic formulation
write.lp(min_cost, "5260_S18_minterm_min_cost.lp",type = 'lp')

# Solve the model
solve(min_cost)

# Make results and sensitivity table 
ps <- get.primal.solution(min_cost)
obj_sa <- get.sensitivity.obj(min_cost)
rhs_sa <- get.sensitivity.rhs(min_cost)

nv <- length(get.variables(min_cost))
mc <- length(get.constr.type(min_cost))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(nv + mc + 1)], 
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(min_cost), colnames(min_cost))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Objective value and sensitivity analysis table Transposing for better quality 
m1<- as.data.frame(sa_tab)
tm1 <- transpose(m1)
setnames(tm1, rownames(m1))
colnames(tm1) <- rownames(m1)
rownames(tm1) <- colnames(m1)
ov
tm1


```

##Graph the Min Cost Solution

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}

# Include solution in edges dataframe
edges$flow <- get.variables(min_cost)
edges$Mincost <- edges$flow * edges$Cost
g <- edges %>%
  # creating igraph: "from" and "to" fields in the first two colums
  select(From, To, ID, Capacity, Cost, Type, flow, Mincost) %>%
  # Make into graph object
  graph_from_data_frame()

#Add route attribute
V(g)$route <- c("From","From","To","To","To","To","To","To","To","To","To")
V(g)$color <- c("gold","green")[1+(V(net)$route=="From")]


# Get some colours in to visualise routes
E(g)$color[E(g)$Type == 'Truck'] <- 'saddlebrown'
E(g)$color[E(g)$Type == 'Airplane'] <- 'forestgreen'
E(g)$color[E(g)$Type == 'Ship'] <- 'royalblue'
E(g)$color[E(g)$Mincost == 0] <- 'white'

g$layout <- matrix(c(-800, -800,  
                       0,  0,  0, 0,  0, 0, 
                       800, 800, 800,
                       225, 125, 
                       300, 250, 200, 150, 100, 50, 
                       250, 175, 100), nc = 2)

get.variables(min_cost)
# Flow as edge size and colour
plot(g, edge.width = 15*E(g)$Mincost/max(E(g)$Mincost), 
     edge.arrow.size=.4,
     edge.label = as.integer(E(g)$Mincost),  vertex.size=35)
#[E(g)$Mincost >= 0]
#vertex.size=24

```

#4 - Last Plan Max Flow with many constraints 

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
#Maximum Flow

# Set up model
max_flow <- make.lp(0, 41)
lp.control(max_flow, sense = "max")

## Set objective fn
obj_fn <- c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1)
set.objfn(max_flow, obj_fn)

# Set up constraints
add.constraint(max_flow, c( 1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),            "<=", 1000000)#inflow
add.constraint(max_flow, c(-1,0,150,240,150,150,240,240,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=",  0 )  #NY
add.constraint(max_flow, c(0,-1,0,0,0,0,0,0,150,240,150,150,240,240,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),  "=",  0)  #FL
add.constraint(max_flow, c(0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0,0,0,0),    "=",  0)  #Lusaka
add.constraint(max_flow, c(0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0,0,0,0,0),"=",  0)  #Libreville
add.constraint(max_flow, c(0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0,0),   "=",  0)  #Nairobi
add.constraint(max_flow, c(0,0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0),   "=",  0)   #Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0,0),"=",  0)  #Luanda
add.constraint(max_flow, c(0,0,0,0,0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0), "=",  0)   #Dakar
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),"=",  0)  #Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0),"=",  0)  #Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,1),"=",  0)  #Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,-1,-1,-1,-1,-1,-1,-1,-1),          "<=", 1000000) #OUtflow

# Air Constraints
add.constraint(max_flow, c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #NY-Lusak
add.constraint(max_flow, c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500) #NY-Nairobi
add.constraint(max_flow, c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500) #NY-Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500) #FL-Lusaka
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 700) #FL-Nairobi
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 600) #FL-Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 200) #Lusaka-Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 0) #Nairobi-Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #Khartoum-Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 140) #Lusaka-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 40 ) #Nairobi-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 80 ) #Khartoum-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 0  ) #Lusaka-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #Nairobi-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0),          "<=", 40 ) #Khartoum-Ndja

# Truck Contraints
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 250) #Lunda-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0),          "<=", 240) #Lunda-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #Lib-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 160) #Lib-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 700) #Dakar-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0),          "<=", 450) #Dakar-Ndjamena

# City REquirements Constraints
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),          "<=", 150000) #Lusaka
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),          "<=", 100000) #Liber
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),          "<=", 120000) #Nairobi
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0),          "<=", 90000) #Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0),          "<=", 130000) #Lunada
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0),          "<=", 50000) #Dakar
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),          "<=", 100000) #Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0),          "<=", 180000) #Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1),          "<=", 80000) #Ndjamena


dimnames(max_flow) <- list(c("Inflow","New York", "Jacksonville","Lusaka", "Libreville", "Nairobi",
                       "Khartoum", "Luanda", "Dakar", "Niamey", "Kosongo", "Ndjamena", "Max Outflow", 
                       "Ny-Lusaka AirC", "NY-Nairobi AirC", "NY-Khartoum AirC", 
                       "JAX-Lusaka AirC", "JAX-Nairobi AirC","JAX-Khartoum AirC", 
                       "Lusaka-Niamey AirC", "Nairobi-Niamey AirC", "Khartoum-Niamey AirC", 
                       "Lusaka-Kosongo AirC","Nairobi-Kosongo AirC", "Khartoum-Kosongo AirC",
                       "Lusaka-Ndjamena AirC", "Nairobi-Ndjamena AirC", "Khartoum-Ndjamena AirC",
                       "Luanda-Kosongo TruckC", "Luanda-Ndjamena TruckC", "Libreville-Kosongo TruckC", 
                       "Libreville-Ndjamena TruckC", "Dakar-Kosongo TruckC", "Dakar-Ndjamena TruckC", 
                       "LusakaR", "LibrevilleR", "NairobiR", "KhartoumR", 
                       "LuandaR", "DakarR", "NiameyR", "KosongoR", "NdjamenaR"),
                       c("I-NY", "I-JAX", as.vector(edges$ID), "Lusaka-O", "Libreville-O", 
                         "Nairobi-O", "Khartoum-O", "Luanda-O","Dakar-O", "Niamey-O",
                         "Kosongo-O", "Ndjamena-O") )

# Write to view the algebraic formulation
write.lp(max_flow, "5260_S18_minterm_max_flow.lp",type = 'lp')

# Solve the model
solve(max_flow)

# Make results and sensitivity table 
ps <- get.primal.solution(max_flow)
obj_sa <- get.sensitivity.obj(max_flow)
rhs_sa <- get.sensitivity.rhs(max_flow)

nv <- length(get.variables(max_flow))
mc <- length(get.constr.type(max_flow))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(nv + mc + 1)], 
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(max_flow), colnames(max_flow))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Objective value and sensitivity analysis table Transposing for better quality 
m2<- as.data.frame(sa_tab)
tm2 <- transpose(m2)
setnames(tm2, rownames(m2))
colnames(tm2) <- rownames(m2)
rownames(tm2) <- colnames(m2)
ov
tm3<- as.data.frame(tm2)
tm3
#get.variables(max_flow)
```

##Graph Max Cost Solution

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
# Include solution in edges dataframe
edges$Mflow <- get.variables(max_flow)[3:32]
edges$TotalAid <- edges$Mflow * edges$Capacity

#create size for vertecies
#V()$Mflow <- get.variables(max_flow)[31:41] #tried playing with size of vertecies but failed
#nodes$Mflow[1] <- get.variables(max_flow)[1]
#nodes$Mflow[2] <- get.variables(max_flow)[2]

g1 <- edges %>%
  # creating igraph: "from" and "to" fields in the first two colums
  select(From, To, ID, Capacity, Cost, Type, Mflow, TotalAid) %>%
  # Make into graph object
  graph_from_data_frame()

#Add route and node attribute
V(g1)$route <- c("From","From","To","To","To","To","To","To","To","To","To")
V(g1)$color <- c("gold","green")[1+(V(net)$route=="From")]
V(g1)$Mflow <- get.variables(max_flow)[31:41] #tried playing with size of vertecies but failed
V(g1)$Mflow[1] <- get.variables(max_flow)[1]
V(g1)$Mflow[2] <- get.variables(max_flow)[2]

# Get some colours in to visualise routes
E(g1)$color[E(g1)$Type == 'Truck'] <- 'saddlebrown'
E(g1)$color[E(g1)$Type == 'Airplane'] <- 'forestgreen'
E(g1)$color[E(g1)$Type == 'Ship'] <- 'royalblue'
E(g1)$color[E(g1)$Mflow == 0] <- 'white'

g1$layout <- matrix(c(-800, -800,  
                       0,  0,  0, 0,  0, 0, 
                       800, 800, 800,
                       225, 125, 
                       300, 250, 200, 150, 100, 50, 
                       250, 175, 100), nc = 2)

plot(g1, edge.width = 20*E(g1)$TotalAid/max(E(g1)$TotalAid) , 
     edge.arrow.size=.3,
     edge.label = as.integer(E(g1)$TotalAid),
     vertex.size= 50*V(g1)$Mflow/max(V(g1)$Mflow))
#get.variables(max_flow)
E(g1)$TotalAid
```

#4 - Last Plan Testing Max Flow by relaxing some constraints to congos

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
#Maximum Flow

# Set up model
max_flow <- make.lp(0, 41)
lp.control(max_flow, sense = "max")

## Set objective fn
obj_fn <- c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1)
set.objfn(max_flow, obj_fn)

# Set up constraints
add.constraint(max_flow, c( 1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),            "<=", 1000000)#inflow
add.constraint(max_flow, c(-1,0,150,240,150,150,240,240,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=",  0 )  #NY
add.constraint(max_flow, c(0,-1,0,0,0,0,0,0,150,240,150,150,240,240,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),  "=",  0)  #FL
add.constraint(max_flow, c(0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0,0,0,0),    "=",  0)  #Lusaka
add.constraint(max_flow, c(0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0,0,0,0,0),"=",  0)  #Libreville
add.constraint(max_flow, c(0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0,0),   "=",  0)  #Nairobi
add.constraint(max_flow, c(0,0,0,0,0,-150,0,0,0,0,0,-150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,150,0,0,0,0,0,1,0,0,0,0,0),   "=",  0)   #Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0,0),"=",  0)  #Luanda
add.constraint(max_flow, c(0,0,0,0,0,0,0,-240,0,0,0,0,0,-240,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,17.7,0,0,0,0,0,1,0,0,0), "=",  0)   #Dakar
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),"=",  0)  #Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0),"=",  0)  #Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-150,-17.7,-150,-150,-17.7,-17.7,0,0,0,0,0,0,0,0,1),"=",  0)  #Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,-1,-1,-1,-1,-1,-1,-1,-1),          "<=", 1000000) #OUtflow

# Air Constraints
add.constraint(max_flow, c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #NY-Lusak
add.constraint(max_flow, c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500) #NY-Nairobi
add.constraint(max_flow, c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500) #NY-Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500) #FL-Lusaka
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 700) #FL-Nairobi
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 600) #FL-Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 200) #Lusaka-Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 0) #Nairobi-Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #Khartoum-Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 140) #Lusaka-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 400 ) #Nairobi-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 500 ) #Khartoum-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 200  ) #Lusaka-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #Nairobi-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0),          "<=", 40 ) #Khartoum-Ndja

# Truck Contraints
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 250) #Lunda-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0),          "<=", 240) #Lunda-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 300) #Lib-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 160) #Lib-Ndjamena
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),          "<=", 700) #Dakar-Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0),          "<=", 450) #Dakar-Ndjamena

# City REquirements Constraints
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0),          "<=", 150000) #Lusaka
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0),          "<=", 100000) #Liber
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0),          "<=", 120000) #Nairobi
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0),          "<=", 90000) #Khartoum
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0),          "<=", 130000) #Lunada
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0),          "<=", 50000) #Dakar
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0),          "<=", 100000) #Niamey
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0),          "<=", 180000) #Kosongo
add.constraint(max_flow, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1),          "<=", 80000) #Ndjamena


dimnames(max_flow) <- list(c("Inflow","New York", "Jacksonville","Lusaka", "Libreville", "Nairobi",
                       "Khartoum", "Luanda", "Dakar", "Niamey", "Kosongo", "Ndjamena", "Max Outflow", 
                       "Ny-Lusaka AirC", "NY-Nairobi AirC", "NY-Khartoum AirC", 
                       "JAX-Lusaka AirC", "JAX-Nairobi AirC","JAX-Khartoum AirC", 
                       "Lusaka-Niamey AirC", "Nairobi-Niamey AirC", "Khartoum-Niamey AirC", 
                       "Lusaka-Kosongo AirC","Nairobi-Kosongo AirC", "Khartoum-Kosongo AirC",
                       "Lusaka-Ndjamena AirC", "Nairobi-Ndjamena AirC", "Khartoum-Ndjamena AirC",
                       "Luanda-Kosongo TruckC", "Luanda-Ndjamena TruckC", "Libreville-Kosongo TruckC", 
                       "Libreville-Ndjamena TruckC", "Dakar-Kosongo TruckC", "Dakar-Ndjamena TruckC", 
                       "LusakaR", "LibrevilleR", "NairobiR", "KhartoumR", 
                       "LuandaR", "DakarR", "NiameyR", "KosongoR", "NdjamenaR"),
                       c("I-NY", "I-JAX", as.vector(edges$ID), "Lusaka-O", "Libreville-O", 
                         "Nairobi-O", "Khartoum-O", "Luanda-O","Dakar-O", "Niamey-O",
                         "Kosongo-O", "Ndjamena-O") )

# Write to view the algebraic formulation
write.lp(max_flow, "5260_S18_minterm_max_flow.lp",type = 'lp')

# Solve the model
solve(max_flow)

# Make results and sensitivity table 
ps <- get.primal.solution(max_flow)
obj_sa <- get.sensitivity.obj(max_flow)
rhs_sa <- get.sensitivity.rhs(max_flow)

nv <- length(get.variables(max_flow))
mc <- length(get.constr.type(max_flow))
ov <- paste0("Objective Value = ", ps[1])

sa_tab <- rbind(ps[2:(nv + mc + 1)], 
                round(c(rhs_sa$duals[1:mc], obj_fn), 2),
                round(c(rhs_sa$dualsfrom[1:mc],obj_sa$objfrom), 2),
                round(c(rhs_sa$dualstill[1:mc],obj_sa$objtill), 2)) 
colnames(sa_tab) <- c(rownames(max_flow), colnames(max_flow))
rownames(sa_tab) <- c("solution", "duals/coef", "Sens From", "Sens Till")      

# Objective value and sensitivity analysis table Transposing for better quality 
m2<- as.data.frame(sa_tab)
tm2 <- transpose(m2)
setnames(tm2, rownames(m2))
colnames(tm2) <- rownames(m2)
rownames(tm2) <- colnames(m2)
ov
tm3<- as.data.frame(tm2)
tm3
#get.variables(max_flow)

```

##Graph Max Cost Solution

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
# Include solution in edges dataframe
edges$Mflow <- get.variables(max_flow)[3:32]
edges$TotalAid <- edges$Mflow * edges$Capacity

#create size for vertecies
nodes$Mflow2 <- get.variables(max_flow)[31:41] #tried playing with size of vertecies but failed
nodes$Mflow2[1] <- get.variables(max_flow)[1]
nodes$Mflow2[2] <- get.variables(max_flow)[2]

g1 <- edges %>%
  # creating igraph: "from" and "to" fields in the first two colums
  select(From, To, ID, Capacity, Cost, Type, Mflow, TotalAid) %>%
  # Make into graph object
  graph_from_data_frame()

#Add route and node attribute
V(g1)$route <- c("From","From","To","To","To","To","To","To","To","To","To")
V(g1)$color <- c("gold","green")[1+(V(net)$route=="From")]
V(g1)$Mflow <- get.variables(max_flow)[31:41] #tried playing with size of vertecies but failed
V(g1)$Mflow[1] <- get.variables(max_flow)[1]
V(g1)$Mflow[2] <- get.variables(max_flow)[2]

# Get some colours in to visualise routes
E(g1)$color[E(g1)$Type == 'Truck'] <- 'saddlebrown'
E(g1)$color[E(g1)$Type == 'Airplane'] <- 'forestgreen'
E(g1)$color[E(g1)$Type == 'Ship'] <- 'royalblue'
E(g1)$color[E(g1)$Mflow == 0] <- 'white'

g1$layout <- matrix(c(-800, -800,  
                       0,  0,  0, 0,  0, 0, 
                       800, 800, 800,
                       225, 125, 
                       300, 250, 200, 150, 100, 50, 
                       250, 175, 100), nc = 2)

plot(g1, edge.width = 20*E(g1)$TotalAid/max(E(g1)$TotalAid) , 
     edge.arrow.size=.3,
     edge.label = as.integer(E(g1)$TotalAid),
     vertex.size= 50*V(g1)$Mflow/max(V(g1)$Mflow))
#get.variables(max_flow)
E(g1)$TotalAid
```

#Appendix for additional igraph data structure

##Fuction to run Matrix

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}



createConstraintsMatrix <- function(edges, total_flow) {

  # Edge IDs to be used as names
  names_edges <- edges$ID
  # Number of edges
  numberof_edges <- length(names_edges)

  # Node IDs to be used as names
  names_nodes <- c(edges$From, edges$To) %>% unique
  # Number of nodes
  numberof_nodes <- length(names_nodes)

  # Build constraints matrix
  constraints <- list(
    lhs = NA,
    dir = NA,
    rhs = NA)

  #Build capacity constraints by flowing through each edge should not be larger than capacity.
  #add zero except the ones that matchs the edge
  
  # Flow through individual edges
  constraints$lhs <- edges$ID %>%
    length %>%
    diag %>%
    set_colnames(edges$ID) %>%
    set_rownames(edges$ID)
  # should be smaller than or equal to
  constraints$dir <- rep('<=', times = nrow(edges))
  # than capacity
  constraints$rhs <- edges$Max


  #' Build node flow constraints For each node, find all edges that go to that node

  nodeflow <- matrix(0,
                     nrow = numberof_nodes,
                     ncol = numberof_edges,
                     dimnames = list(names_nodes, names_edges))

  for (i in names_nodes) {

    # input arcs
    edges_in <- edges %>%
      filter(To == i) %>%
      select(ID) %>%
      unlist
    # output arcs
    edges_out <- edges %>%
      filter(From == i) %>%
      select(ID) %>%
      unlist

    # set input coefficients to 1
    nodeflow[
      rownames(nodeflow) == i,
      colnames(nodeflow) %in% edges_in] <- 1

    # set output coefficients to -1
    nodeflow[
      rownames(nodeflow) == i,
      colnames(nodeflow) %in% edges_out] <- -1
  }


  # Source node is minimum ID number
  # Sink node is  maximum ID number
  sourcenode_id <- min(edges$From)
  targetnode_id <- max(edges$To)
  # Keep node flow values for separate step below
  nodeflow_source <- nodeflow[rownames(nodeflow) == sourcenode_id,]
  nodeflow_target <- nodeflow[rownames(nodeflow) == targetnode_id,]
  # Exclude them from node flow here
  nodeflow <- nodeflow[!rownames(nodeflow) %in% c(sourcenode_id, targetnode_id),]

  # Add nodeflow to the constraints list
  constraints$lhs <- rbind(constraints$lhs, nodeflow)
  constraints$dir <- c(constraints$dir, rep('==', times = nrow(nodeflow)))
  constraints$rhs <- c(constraints$rhs, rep(0, times = nrow(nodeflow)))


  #' Build constraints 

  # Add initialisation to the constraints list
  constraints$lhs <- rbind(constraints$lhs,
                           source = nodeflow_source,
                           target = nodeflow_target)
  constraints$dir <- c(constraints$dir, rep('==', times = 2))
  # Flow should be negative for source, and positive for target
  constraints$rhs <- c(constraints$rhs, total_flow * -1, total_flow)

  return(constraints)
}

#Create My Matrix
constraintsMatrix <- createConstraintsMatrix(edges, 1000000)
#constraintsMatrix

#Set City Requirement 
constraintsMatrix$rhs[31] <- 500000
constraintsMatrix$rhs[32] <- 500000
constraintsMatrix$rhs[33] <- -150000
constraintsMatrix$rhs[34] <- -100000
constraintsMatrix$rhs[35] <- -120000
constraintsMatrix$rhs[36] <- - 90000
constraintsMatrix$rhs[37] <- -130000
constraintsMatrix$rhs[38] <- -180000
constraintsMatrix$rhs[39] <- -80000


#Review data for Validity
CM <- as.data.frame(constraintsMatrix)
#glimpse(CM)
#CM 
write.csv(CM, file = "MyData.csv")
#constraintsMatrix$lhs
#constraintsMatrix$dir
#constraintsMatrix$rhs

#plot.lpExtPtr(min_cost)
#get.variables(min_cost)
```

#Using I graph to calculate min and max (didnt work)

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
#Addmore attributes to the Graph

E(net)$Group <- E(net)$Type 
#E(net)$Group
#V(net)$Group <- V(net)$CityType 
#V(net)$Group
E(net)$weight = E(net)$Capacity
#E(net)$weight 
E(net)$name = E(net)$ID
#E(net)$name 
V(net)$weight = V(net)$Requirements
#V(net)$weight
E(net)$capacity <- E(net)$Max
E(net)$cost <- E(net)$Cost
plot(net, edge.label = E(net)$Max)
plot(net, edge.label = E(net)$Cost)
# Testing  Maximum flow
g_max <- max_flow(net, c("New York, NY", 'Jacksonville, FL'), 
                   c('Kosongo, D.R. Congo' ,"Ndjamena, Chad",
                     'Niamey, Niger'))
g_max$value
g_max
gx <- net
E(gx)$label <- g_max$flow
plot(gx)


min_cut(net, c("New York, NY", 'Jacksonville, FL'), 
                   c('Kosongo, D.R. Congo' ,"Ndjamena, Chad",
                     'Niamey, Niger'))
max_flow(net, c("New York, NY", 'Jacksonville, FL'), 
                   c('Kosongo, D.R. Congo' ,"Ndjamena, Chad",
                     'Niamey, Niger'))$value
summary(net) #find more info
net[] #for matrix
degree(net)
E(net)[]
V(net)[]

test<- net[]
test<- as.data.frame(as.matrix(test))
library(data.table)
library(reshape2)
test1<- data.table(test)

test1 <- transpose(test, fill =NA)
test1 <- melt(test1, fill = 0)
test1

```